Deep Learning

### 2015-01-31 deepreview.tex
more audience-adaptation, sec. 3

From the earliest days of pattern recognition~\citep{selfridge,Rosenblatt57}
researchers aimed to replace hand-engineered features by multiple layers of
learned features.  This was eventually achieved by using the
backpropagation algorithm which was discovered independently by several
different groups in the 1970s and 1980s~\citep{Werbos74,Parker85,LeCun85,RHW}.  
Backpropagation is simply an application of
the chain rule of derivatives (Figure~\ref{fig:backprop-box}),
which yields an efficient way of computing the gradient of a
smooth objective function with respect to all of the weights 
%% and parameters 
%% FOR THE NOVICE READER INCLUDING BOTH WEIGHTS AND "PARAMTERS" IS CONFUSING.
%% ITS BETTER TO SAY SOMETHING CLEARER EVEN IF IT IS LESS GENERAL OR CORRECT.
in  a layered network (Figure~\ref{fig:backprop-box}). 
The objective function typically measures an error to be minimized: 
the discrepancy between
the actual output of the network on a given training case and the target
output for that case.  The key insight is that the error derivatives with
respect to the {\it ouputs} of a layer can be computed by working
backwards from the error derivatives with respect to its {\em inputs}
to the subsequent layer.
%% THE TRICKY STEP IS COMPUTING dE/dOUT FROM dE/dIN IN THE SUBSEQUENT
%% LAYER.  I THINK WE SHOULD FOCUS ON GETTING OVER THAT IDEA FIRST.
%%  I PLAN TO REDO THE FIGURE TO MAKE IT SIMPLER.  ITS MUCH TOO
%%  CONFUSING FOR A NOVICE AT PRESENT.  WE SHOULD HAVE A SEPARATE
%%  DISCUSSION OF THAT.
Once this backwards recursion has been used to compute
error derivatives for the outputs of all layers, it is easy to compute
error derivatives for the incoming weights of the neurons in each layer 
(Figure~\ref{fig:backprop-box}).

>>>>

From the earliest days of pattern recognition~\citep{selfridge,Rosenblatt57}
researchers aimed to replace hand-engineered features by multiple layers of
learned features.  This was eventually achieved by using the
backpropagation algorithm which was discovered independently by several
different groups in the 1970s and 1980s~\citep{Werbos74,Parker85,LeCun85,RHW}.  
The gradient of an objective function with respect to the network
weights tells us how a change in each of the weights would influence
the final error (top left of Figure~\ref{fig:backprop-box}).
Gradient descent changes the weights accordingly, in the direction of the
gradient, towards reducing the error.
Backpropagation is simply an application of
the chain rule of derivatives 
which yields an efficient way of computing this gradient in
a deep neural network (or any other composition of differentiable operations).
%% FOR THE NOVICE READER INCLUDING BOTH WEIGHTS AND "PARAMTERS" IS CONFUSING.
%% ITS BETTER TO SAY SOMETHING CLEARER EVEN IF IT IS LESS GENERAL OR CORRECT.
The objective function being minimized typically measures an error to be minimized: 
the discrepancy between
the actual output of the network on a given training case and the target
output for that case.  The key insight is that the error derivatives with
respect to the {\it ouputs} of a layer can be computed by working
backwards from the error derivatives with respect to its {\em inputs}
to the subsequent layer.
%% THE TRICKY STEP IS COMPUTING dE/dOUT FROM dE/dIN IN THE SUBSEQUENT
%% LAYER.  I THINK WE SHOULD FOCUS ON GETTING OVER THAT IDEA FIRST.
%%  I PLAN TO REDO THE FIGURE TO MAKE IT SIMPLER.  ITS MUCH TOO
%%  CONFUSING FOR A NOVICE AT PRESENT.  WE SHOULD HAVE A SEPARATE
%%  DISCUSSION OF THAT.
Once this backwards recursion has been used to compute
error derivatives for the outputs of all layers, it is easy to compute
error derivatives for the incoming weights of the neurons in each layer 
(Figure~\ref{fig:backprop-box}).
